### 2010-06-30 trunk/paper/IIWAS2010/content/system_arch.tex
current latest, changed need to be made

QRM contains the necessary  
information required to re-run this procedure.Once we have 
relevant QRMs through QRM ranking for a given user query, we can  
get answers by re-running the pathways with help of 
the \emph{Query Resolution Engine} (QRE) of Morpheus.

>>>>

Once we have relevant QRMs through QRM ranking for a given user query, we can get answers by re-running the pathways with help of the \emph{Query Resolution Engine} (QRE) of Morpheus. The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, and highlighting of datato form a text answer.

%When a user submits a new query to the Morpheus system, one or more stored QRMs are executed to obtain results. A QRM contains an XML script representing an algorithm that will obtain the required result. The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, highlighting data, cutting and pasting text, and constructing an answer in the form of a text string. There is greater complexity in dealing with web forms than with links. At present, the GET form submission method is used. This means that in preparation to submit a form, the Morpheus System builds a querystring consisting of name-value pairs. For a given form, there may be text fields, drop-down boxes, and among other components. In order to support form submission in such circumstances, the QRE performs different actions based upon the input type. For text fields, simply adding a key/value pair to the query string suffices. For a drop-down box, the QRE extracts the form element to find the appropriate value to include in the query string. It does this by examine each option in the drop-down and matching the user’s input to the text field in the option. The value attribute of the option is then added to the querystring. The value and text attributes of a dropdown option might be the same, but they are not guaranteed to be. All input data are kept in an internal table. The QRM script contains keys that allow the QRE to map SSQ inputs from the table to the appropriate form inputs. Furthermore, highlighted text segments collected during execution of the script are stored in the table. Once all actions in the script have been carried out, the QRE returns the textual answer this process has created. This answer is then be rendered in a browser displayed to the user.
